---
title: "Simple document"
author: Mia Isaacs
date: 2024-09-10
output: github_document
---

```{r, echo = FALSE, message = FALSE}
library(tidyverse)
```

Loaded necessary packages (e.g. `tidyverse`).


I'm an R Markdown document! 

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.

# Learning Assessment

The chunk below creates a dataframe containing a sample of size 500 from a 
random normal variable, constructs the specified logical vector, takes the 
absolute value of each element of that sample,and produces a histogram of 
the absolute value. The code chunk also finds the median of the sample and
stores it for easy in-line printing.

```{r learning_assessment_1}
library(tidyverse)

la_df = 
  tibble(
   norm_samp = rnorm(500, mean = 1),
   samp_g0 = norm_samp > 0,
   abs_v_samp = abs(norm_samp)
 )


ggplot(la_df, aes(x = abs_v_samp)) + 
  geom_histogram()


median_samp = median(pull(la_df, norm_samp))
```

The median of the variable containing absolute values is 
`r round(median_samp, digits = 2)`.


# Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell
